The Globular Cluster System of the Auriga Simulations

### 2019-06-12 AurigaGCS.tex
More paragraphs for the introduction. Now reached paragraph focusing on (globular) star cluster formation in zoom simulations

\section{Introduction}
Globular clusters (GC)s are old, bright, ubiquitous, and various properties of
GC systems show correlations with their host galaxies. GC systems are believed to
retain information about the galactic (gas) conditions at times of formation,
thus, could offer unique insight into the chemodynamical evolution of their 
parent galaxies, if the formation and evolution of GCs- and GC systems themselves 
is adequately understood. However, despite decades of research (the extensive 
literature on GCs is summarised in several books and review articles, e.g.~\citealt{
1991ARA&A..29..543H, Harris2001, 2004Natur.427...31W, 2006ARA&A..44..193B, 
2012A&ARv..20...50G, 2014CQGra..31x4006K, 2018RSPSA.47470616F}), consensus on an 
exhaustive picture of the formation of GCs is yet to be reached.

The literature offers a wealth of formation scenarios. \citet{1968ApJ...154..891P}
and \citet{1984ApJ...277..470P} argue that GCs form as the earliest bound
structures in the Universe (i.e. prior to formation of the main galaxy), 
noting that the Jeans length and mass shortly after recombination is consistent
with typical GC masses and sizes. Alternative models suggest that GCs form during
formation of proto-galaxies, for example as a result of thermal instabilities
in hot gas-rich haloes \citep{1985ApJ...298...18F}, or triggered by other mechanisms
such as shock compression or cloud-cloud colissions \citep[e.g.][]{
1980glcl.conf..301G, 1992ApJ...400..265M, 1996ASPC...92..241L, 1994ApJ...429..177H,
2001ApJ...560..592C}.

Yet another hypothesis is that star cluster formation is triggered by (major) 
gas-rich galaxy mergers \citep{1987nngp.proc...18S, 1992ApJ...384...50A},
which is naturally expected within the framework of hierarchical assembly. One
testable prediction of this scenario is the formation of young clusters in
interacting and merging galaxies, which has been observed and show remarkable
similarities with globulars in the Milky Way \citep[e.g.][]{1995AJ....109..960W, 
1996AJ....112..416H, 1999AJ....118..752Z, 1999AJ....118.1551W}. Moreover, models
that test this hypothesis yield GC populations consistent with various 
observables \citep[e.g.][]{2010ApJ...718.1266M, 2018MNRAS.480.2343C}, and
the recent numerical simulation of an isolated dwarf-dwarf merger executed at 
very high resolution (baryonic mass $m_b \sim$~4M\Sun; softening $\epsilon = 0.1$) 
produce promising star clusters that could be globular progenitors \citep{2019arXiv190509840L}.

More recent modelling efforts combine various aspects from the aforementioned
formation channels \citep[e.g.][]{2000ApJ...533..869C, 2002ApJ...567..853C, 2002MNRAS.333..383B,
2003egcs.conf..224G}

Previous studies
\citep{2005ApJ...623..650K}
\citep{2016ApJ...831..204R}
\citep{2017ApJ...834...69L}
\citep{2017MNRAS.465.3622R}
\citep{2018MNRAS.474.4232K}
\citep{2018MNRAS.475.4309P,2019MNRAS.486.3134K}

>>>>

\section{Introduction}
Globular clusters (GC)s are old, bright, ubiquitous, and various properties of
GC systems show correlations with their host galaxies. GC systems are believed to
retain information about the galactic (gas) conditions at times of formation,
thus, could offer unique insight into the (chemodynamical) evolution of their 
parent galaxies, if the formation and evolution of GCs- and GC systems themselves 
is adequately understood. However, despite decades of research (the extensive 
literature on GCs is summarised in several books and review articles, e.g.~\citealt{
1991ARA&A..29..543H, Harris2001, 2004Natur.427...31W, 2006ARA&A..44..193B, 
2012A&ARv..20...50G, 2014CQGra..31x4006K, 2018RSPSA.47470616F}), consensus on an 
exhaustive picture of the formation of GCs is yet to be reached.

The literature offers a wealth of formation scenarios. \citet{1968ApJ...154..891P}
and \citet{1984ApJ...277..470P} argue that GCs form as the earliest bound
structures in the Universe (i.e. prior to formation of the main galaxy), 
noting that the Jeans length and mass shortly after recombination is consistent
with typical GC masses and sizes. \citet{2005MNRAS.364..367D} and \citet{
2009ApJ...706L.192B} argue that (the blue subpopulations of) GCs form in biased 
dark matter halos at high redshift. Other recent hypotheses of GC formation prior 
to collapse of the proto-galaxy include formation in colliding supershells 
\citep{2017Ap&SS.362..183R}, in supersonically induced gaseous objects
\citep{2019arXiv190408941C}, or in high-speed collisions of dark matter subhaloes
\citep{2019arXiv190508951M}. \citet{2017MNRAS.472.3120B} suggests
that (the blue subpopulation of) GCs could form in high density regions along
the cosmic filament before or during collapse.

Other models also date GCs formation during formation of the proto-galaxy itself,
for example as a result of thermal instabilities in hot gas-rich haloes 
(\citealt{1985ApJ...298...18F}, also see the discussions in \citealt{
1990ApJ...363..488K}). Alternative formation trigggers are also explored, such as 
(other causes of) shock compression, or cloud-cloud colissions \citep[e.g.][]{
1980glcl.conf..301G, 1992ApJ...400..265M, 1994ApJ...429..177H, 1995ApJ...442..618V,
1996ASPC...92..241L, 2001ApJ...560..592C}.

Yet another hypothesis is that star cluster formation is triggered by (major) 
gas-rich (spiral) galaxy mergers \citep{1987nngp.proc...18S, 1992ApJ...384...50A},
which is naturally expected within the framework of hierarchical assembly. One
testable prediction of this scenario is the formation of young clusters in
interacting and merging galaxies, which has been observed and are found to show 
remarkable similarities with globulars in the Milky Way \citep[e.g.][]{
1995AJ....109..960W, 1996AJ....112..416H, 1999AJ....118..752Z, 1999AJ....118.1551W}.
Moreover, modelling efforts of this framework yield GC (sub)populations consistent 
with various observables \citep[e.g.][]{2010ApJ...718.1266M, 2018MNRAS.480.2343C}, 
and the recent numerical simulation of an isolated dwarf-dwarf merger executed at 
very high resolution (baryonic mass $m_b \sim$~4M\Sun; softening $\epsilon = 0.1$) 
produce star clusters that could be globular progenitors \citep{
2019arXiv190509840L}.

As for the formation timeline, the scenarios (and flavours thereof) of \citet{
1985ApJ...298...18F} and \citet{1992ApJ...384...50A} are intertwined because
accretion and mergers continuously occurs trough out hierarchical build-up of
galaxies. Various (other) hierarchical formation channels thus combine different
aspects of the aforementioned paradigms, such as GC formation in (small) galactic
disks before they are accreted onto an assembling galaxy \citep[e.g.][]{
2000ApJ...533..869C, 2002ApJ...567..853C, 2002MNRAS.333..383B, 2003egcs.conf..224G}. 
We refer to \citet{2001astro.ph..8034G} for a scoreboard of the aforementioned 
paradigms compared to observations of the Milky Way globular cluster system.

% Rosenblatt+ 1988, Cen 2001, Bromm \& Clarke 2002, Diemand+ 2002, Moore+ 2006,
% Boley+ 2009, Griffen+ 2010, Trenti+ 2015, Kimm+ 2016, Ricotti+ 2016, Boylan-Kolchin 2017,
% Creasey+ 2019.

We now turn to recent studies that focus on the hypothesis that the physical 
processes responsible for the formation of young massive clusters (YMC)s (observable)
in the local Universe also governs GC formation at high redshifts and differences
between both classes of objects are caused by nearly a Hubble time of (dynamical)
evolution. This picture is based on observed similarities between YMCs and GCs
\citep[e.g.][]{1992AJ....103..691H}, % Schweizer+ 1996, Whitmore+ 1999, Bastian+ 2006
and strengthened by observations of gravitationally lensed objects at high redshifts
($z = 2-6)$. These sources have properties reminiscent of (local) YMCs and may be
GC progenitors at times of formation (Vanzella et al. 2017; Johnson et al. 2017).
Early modelling work by \citet{2015MNRAS.454.1658K} is now incorporated into
cosmological zoom simulations and shows promising results
\citep{2018MNRAS.475.4309P,2019MNRAS.486.3134K}.

Recent studies by other groups also incorporate formation of (globular) star 
clusters into cosmological zoom simulations.
\todo[inline]{
Cosmological Galform simulations (e.g. Oser et al. 2010; Cook et al. 2016; 
Rodriguez-Gomez et al. 2016), in situ vs. ex situ, particle tagging.}

\citep{2005ApJ...623..650K}
\citep{2016ApJ...831..204R}
\citep{2017ApJ...834...69L}
\citep{2017MNRAS.465.3622R}
\citep{2018MNRAS.474.4232K}
\citep{2018MNRAS.475.4309P,2019MNRAS.486.3134K}

\citep{2010ApJ...718.1266M,2014ApJ...796...10L,2018MNRAS.480.2343C,
2019MNRAS.486..331C,2019arXiv190505199C}

% bimodality in the broad-band colours of many (perhaps most) GC systems (e.g.
% Zepf & Ashman 1993; Elson, Santiago & Gilmore 1996; Geisler,
% Lee & Kim 1996; Forbes, Brodie & Huchra 1997a; Gebhardt &
% Kissler-Patig 1999; Kundu & Whitmore 2001; Larsen et al. 2001).
